I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-19 Paper/proofs.tex

	\begin{lemma}[Sign]
		\label{lemma1}
		Let $L,L'$  consecutive layers of a DNN without compensation, 
		and $m\in L$ $n\in L'$. Then if both 
		$w(m n) \neq 0$ and $S(n) \neq 0$, then 
		$S(m)=S(n)\mathrm{Sign}(W_{n m})$.
	\end{lemma}

@@

				\begin{lemma} \label{lem:open_node_2}
					A node $b$ in the hidden layer will not be in a weak compensating path if and only if one of the following two happens:
					\begin{enumerate}
					  	\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $W_{b,z}=0$ to denote this case, or
						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $W_{a_j,b}=0$ to denote this case.
					\end{enumerate}

>>>>

\begin{lemma}[Sign]
	\label{lemma1}
	Let $L,L'$  consecutive layers of a DNN without compensation, 
	and $m\in L$ $n\in L'$. Then if both 
	$W_{nm} \neq 0$ and $S(n) \neq 0$, then 
	$S(m)=S(n)\mathrm{Sign}(W_{n m})$.
\end{lemma}

@@

			\begin{lemma} \label{lem:open_node_2}
				A node $b$ in the hidden layer will not be in a weak compensating path if and only if one of the following two happens:
				\begin{enumerate}
					\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $weight({bz})=0$ to denote this case, or
					\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $weight({a_jb})=0$ to denote this case.
				\end{enumerate}
